---
title: "Code book"
author: "Monica Zurita"
date: "10/22/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r load-packages, include=FALSE}
library(dplyr)
library(base)
```

```{r}
source("run_analysis.R", local = knitr::knit_global())
```


## Getting and Cleaning Data
### Course Project


This assignment correspond to the project developed in Getting and Cleaning Data.

This project employs Human Activity Recognition Using Smartphones
 Data Set from the UCI Machine Learning Repository
 
The data is divided in two sets: training an test, so, the first step is merging both sets.  However, before merging, the data must be reading using the read.table command.

For checking the dimensions the command dim could be employed:

```{r X_test, X_train}
dim(X_test)
dim(X_train)
```
Since both have same dimension with rbind command both data sets are merged.  Same treatment is performed to y and subject data sets.

Features file has 561 files and 2 columns and provides the names of the x data set's columns by the colnames command.  Before merging x with y and subject data sets, the last two data sets are also named by same column.

Using grep command, mean and std columns of x data set could be obtained.  The data to be employed must include:

```{r features, mean_std_col}
features[mean_std_col,]
```
After extracting the columns of mean and SD of x data set, the merge with y and subject columns is performed by cbind command.

Employing factor and levels commands, the numbers in activity column are changed to the labels ("WALKING, SITTING, etc.)

Finally, a new data set is created by summarizing the mean of the variables grouped by subject and activity label.

```{r tidy_data}
head(tidy_data)
```

